Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-12-12 manuscript/manuscript.tex
Spell check and correction
Working on JY's comments.

\item There are 41 columns (fields) of data for each row, with each
  row representing a single SR. To facilitate 
  processing, column names were made lower case and 
  spaces were replaced with underscores, e.g. \texttt{complaint\_type}. 
  This naming convention is used throught this paper.

@@

During the 10-year period from 2014 to 2023,  NYC's 311 system
experienced a 50\% increase in the number of SRs, 
reflecting a growing public reliance on and usage of 
the 311 system. (During this 10-year time-frame, the 
population of NYC grew just 0.6\%.). The most significant increase
in activity occurred in 2020, when the volume of requests 
surged to 3.23 million during the COVID-19 pandemic, 
illustrating the essential role of the 311 system in supporting 
NYC residents during times of crisis. This steady 
rise in SRs can be at least partially attributed to the increased 
accessibility of the 311 system via online and mobile 
platforms, as well as heightened public awareness of the service. 
While the spike in 2020 was exceptional, the broader trend 
indicates sustained growth in SR volume in future years,  
highlighting the system's expanding role in managing 
both routine City operations and extraordinary events.

Figure~\ref{fig:SRcountbyAgency} provides a breakdown of SRs by
the responsible Agency, showing the cumulative 
percentage of SRs handled by each
agency over the 2-year time-frame. Note that the
distribution of SRs is heavily concentrated among a few key 
agencies. The six largest agencies are:

@@

The \textit{Mostly Empty} category includes fields such as
\texttt{taxi\_company\_borough}, \texttt{due\_date},
\jy{These variables seem only relevant to certain agencies, which
  could be made available in a separate table.}
\texttt{road\_ramp}, and \texttt{bridge\_highway\_name}.
The \textit{Partially Empty} category includes fields such as
\texttt{location\_type}, \texttt{landmark}, 
and \texttt{cross\_street\_1 \& \_2}. And the \textit{Few/None Empty} 
category includes \texttt{created\_date}, \texttt{complaint\_type},
\texttt{agency}, and \texttt{status}. For some analysis efforts, it may be
prudent to inquire further as to why some fields are 
mostly or almost always blank. Figure~\ref{fig:blank_fields} is 
a graphic depiction of total empty (blank \& N/As) for each 
field illustrating the grouping into 
the Most, Partial, and Few/None categories.

@@

\jy{Could refer to cross-plotform data format such as Arrow
  \citep{bates2024csv}.}

>>>>

\item There are 41 columns (fields) of data for each row, with each
  row representing a single SR. To facilitate 
  processing, column names were made lower case and 
  spaces were replaced with underscores, e.g. \texttt{complaint\_type}. 
  This naming convention is used throughout this paper.

@@

During the 10-year period from 2014 to 2023,  NYC's 311 system
experienced a 50\% increase in the number of SRs, 
reflecting a growing public reliance on and usage of 
the 311 system. (During this 10-year time frame, the 
population of NYC grew just 0.6\%.). The most significant increase
in activity occurred in 2020, when the volume of requests 
surged to 3.23 million during the COVID-19 pandemic, 
illustrating the essential role of the 311 system in supporting 
NYC residents during times of crisis. This steady 
rise in SRs can be at least partially attributed to the increased 
accessibility of the 311 system via online and mobile 
platforms, as well as heightened public awareness of the service. 
While the spike in 2020 was exceptional, the broader trend 
indicates sustained growth in SR volume in future years,  
highlighting the system's expanding role in managing 
both routine City operations and extraordinary events.

Figure~\ref{fig:SRcountbyAgency} provides a breakdown of SRs by
the responsible Agency, showing the cumulative 
percentage of SRs handled by each
agency over the 2-year time frame. Note that the
distribution of SRs is heavily concentrated among a few key 
agencies. The six largest agencies are:

@@

The \textit{Mostly Empty} category includes fields such as
\texttt{taxi\_company\_borough}, \texttt{due\_date}
\texttt{road\_ramp}, and \texttt{bridge\_highway\_name}.

Of particular note is that several of the \textit{Mostly Empty} fields
are used by only one or two Agencies. Example:

The \textit{Partially Empty} category includes fields such as
\texttt{location\_type}, \texttt{landmark}, 
and \texttt{cross\_street\_1 \& \_2}.

And the \textit{Few/None Empty} 
category includes \texttt{created\_date}, \texttt{complaint\_type},
\texttt{agency}, and \texttt{status}.

For some analysis efforts, it may be prudent to inquire 
further as to why some fields are mostly or almost 
always blank. Figure~\ref{fig:blank_fields} is 
a graphic depiction of total empty (blank \& N/As) for each 
field illustrating the grouping into the Most, 
Partial, and Few/None categories.

@@

\jy{Could refer to cross-platform data format such as Arrow
  \citep{bates2024csv}.}
